---
title: "互联网地图学 — ex 3"
author: "Jianghao Wang"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    theme: architect # architect cayman leonids tactile hpstr
    highlight: github # vignette github
    toc: true
    toc_depth: 4
    number_sections: true
---

# Mapping with leaflet + R

## Markers
利用经纬度坐标来标记地图上的点。可以输入的类型包括

- `SpatialPoints` or `SpatialPointsDataFrame` objects (from the `sp` package)
- `POINT`, `sfc_POINT`, and `sf` objects (from the `sf` package); only `X` and `Y` dimensions will be considered
- Two-column numeric matrices (first column is longitude, second is latitude)
- Data frame with latitude and logitude columns. You can explicitly tell the marker function which columns contain the coordinate data (e.g. `addMarkers(lng = ~Longitude, lat = ~Latitude)`), or let the function look for columns named `lat`/`latitude` and `lon`/`lng`/`long`/`longitude` (case insensitive).
- Simply provide numeric vectors as `lng` and `lat` arguments

一个简单的实例

```{r warning=FALSE}
library(leaflet)
data(quakes)
head(quakes)
# Show first 20 rows from the `quakes` dataset
leaflet(data = quakes[1:20,]) %>% addTiles() %>%
  addMarkers(~long, ~lat, popup = ~as.character(mag), label = ~as.character(mag))
```

Marker Clusters

```{r fig.height=4, message=FALSE}
leaflet(quakes) %>% addTiles() %>% addMarkers(
  clusterOptions = markerClusterOptions()
)
```


## Points

```{r fig.height=4}
leaflet(quakes) %>% addTiles() %>% addCircleMarkers()
```

Or customize their color, radius, stroke, opacity, etc.

```{r fig.height=4, message=FALSE, warning=FALSE}
# Create a palette that maps factor levels to colors
pal <- colorFactor(c("navy", "red"), domain = c("ship", "pirate"))
quakes$type <-  factor(ifelse(runif(nrow(quakes)) > 0.75, "pirate", "ship"),c("ship", "pirate"))

leaflet(quakes) %>% addTiles() %>%
  addCircleMarkers(
    radius = ~ifelse(type == "ship", 6, 10),
    color = ~pal(type),
    stroke = FALSE, fillOpacity = 0.5
  )
```

```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
aqi <- read.csv("data/aqi.csv")
pal <- colorQuantile("YlOrRd", NULL, n=5)
leaflet(aqi) %>% addTiles()%>% 
  addCircleMarkers(~lon, ~lat , popup=aqi$PM25,
                   radius = log2(aqi$PM25),
                   stroke = FALSE, fillOpacity = 0.8,
                   color= ~pal(AQI)) 
```

## Lines

```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
# install.packages("sf")
library(sf)

china <- read_sf("data/china.shp")

plot(china)
leaflet(data = china) %>%
    addTiles() %>%
    addPolylines()
```
    
## Polygon

```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
china$id <- as.numeric(china$id)
china$id <- rnorm(n = nrow(china), mean = 100, sd = 5)
leaflet(data = china) %>%
    addTiles() %>%
    addPolygons(fillColor = ~colorQuantile("YlOrRd", id)(id), 
                color = "#444444", weight = 1, smoothFactor = 0.5,
                opacity = 1.0, fillOpacity = 0.7,
                highlightOptions = highlightOptions(color = "white", weight = 2,
                                                    bringToFront = TRUE))
```

## Raster

```{r fig.height=7, fig.width=7, message=FALSE, warning=FALSE}
# install.packages("raster")
library(raster)

r <- raster("data/oisst-sst.nc")
pal <- colorNumeric(c("#0C2C84", "#41B6C4", "#FFFFCC"), values(r),
  na.color = "transparent")

leaflet() %>% addTiles() %>%
  addRasterImage(r, colors = pal, opacity = 0.8) %>%
  addLegend(pal = pal, values = values(r),
    title = "Surface temp")
```